Wavefield Reconstruction Inversion: an example

### 2020-02-23 repro/papers/wri1d/paper.tex
near final

Note that $L$ is independent of $\alpha$ (definition \ref{eqn:defL},
and for small enough $\alpha$, $\beta > 0$ (definition
\ref{eqn:defbeta}. Conclude that the region $|c-c_*| > L\lambda$ is
independent of $L$, and the minimizer of $J_{\rm
  WRI}[c,\dl,\wl\delta(\cdot-z_s)]$ is $c=c_{\rm min}$ for small
enough $\alpha$. Therefore taking $\alpha$ small does not change the
multimodal nature of $J_{\rm WRI}^{\alpha}$: there remain multiple far-apart
local minima, no matter how small $\alpha$ may be.

>>>>

Note that $L$ is independent of $\alpha$ (definition \ref{eqn:defL}),
and for small enough $\alpha$, $\beta > 0$ (definition
\ref{eqn:defbeta}). Conclude that the region $\{c \in [c_{\rm min},
c_{\rm max}]: |c-c_*| > L\lambda$ is
independent of $\alpha$, and the minimizer of
$J_{\rm WRI}[c,\dl,\wl\delta(\cdot-z_s)]$ in this region (away from
$c_*$) is $c=c_{\rm min}$ for small enough $\alpha$. Therefore taking
$\alpha$ small does not change the multimodal nature of
$J_{\rm WRI}^{\alpha}$: there remain multiple far-apart local minima,
no matter how small $\alpha$ may be.
